### 2012-02-02 GUIErrorDetector/paper/abstract.tex
improve introduction / abstract, and correct the wordings

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Heavy use of reflection in modern GUI applications makes existing
call graph construction algorithms fail to build a sufficiently complete
and precise call graph. Thus, we present a combined RTA and k-CFA
call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.

We implemented our technique and instantiated it on four popular GUI
platforms: SWT, Eclipse plugin development framework, Java Swing, and
Android. In an evaluation on XX subjects over XXX LOC, our technique
found a number of real-world errors, suggesting its effectiveness
and showing good scalability.

>>>>

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Standard call graph construction algorithms fail to build a good
call graph for some modern GUI applications, because of heavy use of reflection.
Thus, we present a method to build reflection-aware call graphs.

We implemented our technique and instantiated it for four popular Java GUI
platforms: SWT, the Eclipse plugin development framework, Swing, and
Android. In an evaluation on 9 programs comprising 67000 LOC, our technique
found both previously-known and unknown errors.

### 2012-02-02 GUIErrorDetector/paper/technique.tex
improve introduction / abstract, and correct the wordings

This section formulates the problem. We define the
notations of \textit{UI thread}, \textit{non-UI threads},
\textit{UI-accessing methods},
 \textit{safe methods}, and \textit{invalid thread access error}, and
two assumptions we make with regard to error detection.

@@

\noindent {\textsc{\textbf{Assumption 1.}}} {We assume that each multithreaded
GUI application has a single global UI thread. This is true for applications
built on top of GUI frameworks adapting the single-GUI-thread rule. The
only exception is that 
 an application may fork a new process to launch another
application with its own UI thread. In that case, we require the new
launched application to be analyzed separately.}\vspace{1mm}

@@

\noindent  {\textsc{\textbf{Definition 4 (Safe Methods).}}} {GUI frameworks that
adopt the single-GUI-thread rule must provide methods to permit non-UI threads
to run code in the UI thread. We can such methods \textit{safe methods}, since
they can be invoked safely by any thread.}\vspace{1mm}

\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
thread access error occurs when the UI thread spawns a non-UI thread, and there
exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
without going through any safe method. }\vspace{2mm}

@@

Our algorithm in Figure~\ref{fig:detectalgorithm} %works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes, UI-accessing nodes, and safe nodes
for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
As an example, for a SWT desktop application, the entry nodes include
the single main method, UI-accessing nodes include all methods that
call method \CodeIn{Display.checkWidget} or \CodeIn{Display.checkDevice},
and safe methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
\CodeIn{Display.syncExec} for message passing. The detailed instantiation
for each supported framework is explained in Section~\ref{sec:platforms}.

For each entry node, the algorithm uses standard Breadth First Search (BFS)
to find all reachable \CodeIn{Thread.start()} nodes (line 7).
Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
non-UI thread is spawned.  After that, from each \CodeIn{Thread.start()}
node, the algorithm uses BFS again to find reachable UI-accessing methods (lines 9 -- 28).
Specifically, it uses a queue to keep track of nodes to be visited (line 9),
and also stores all visited nodes to avoid infinite loop (line 10).
The algorithm checks every successive node to be visited (line 18);
it reports an error if that node is a UI-accessing method (lines 20, 21), or skips
it if it is a safe method (lines 22, 23), or simply keeps traversing otherwise (line 25).

Note that when the algorithm determines that a UI-accessing method may be invoked
by a non-UI thread, it computes full method call chain from the entry node to
the UI-accessing node as the error report.
The method \CodeIn{createErrorReport} on line 20 does that. 
As an example, the method call chain for the error in in Figure~\ref{fig:androiderror}
is shown in Figure~\ref{fig:report}.

Our algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
for potential error-revealing paths, since BFS permits to produce
small error reports (i.e., shorter method call chains). However,
other graph search strategies such as Depath-First Search (DFS) or
exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
we empirically compared different graph search strategies, and demonstrate that
using BFS allows the algorithm to find more errors than DFS and
exhaustive path search.

\begin{figure}[t]
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a set of potential invalid thread access $\mathit{errors}$\\
%\textbf{Auxiliary Methods:}\\
%getSuccNodes($\mathit{g}$, $\mathit{n}$): return node $\mathit{n}$'s successive
%nodes in the graph $\mathit{g}$\\
\vspace{-4mm}
\begin{algorithmic}[1]
\STATE $\mathit{errors}$ $\leftarrow$ $\emptyset$
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
\STATE $\mathit{uiAccessNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
\STATE $\mathit{safeNodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)
\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
\STATE $\mathit{threadStartNodes}$ $\leftarrow$ getReachableStartsByBFS($\mathit{cg}$)
\FOR{each $\mathit{threadStart}$ in $\mathit{threadStartNodes}$}
\STATE $\mathit{queue}$ $\leftarrow$ an empty queue\\
\COMMENT{keep all visited nodes to avoid infinite loop}
\STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
\STATE $\mathit{queue}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
\WHILE{$\mathit{queue}$.isNotEmpty()}
\STATE $\mathit{node}$ $\leftarrow$ $\mathit{queue}$.dequeue()
\IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
\STATE continue
\ENDIF
\STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
\FOR{each $\mathit{succNode}$ in getSuccNodes($\mathit{cg}$, $\mathit{node}$)}
\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessNodes}$}
\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{entryNode, succNode}$)
\STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeNodes}$}
\STATE continue
\ELSE
\STATE $\mathit{queue}$.enqueue($\mathit{succNode}$)
\ENDIF 
\ENDFOR
\ENDWHILE
\ENDFOR
\ENDFOR
\RETURN $errors$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\caption{Algorithm for detecting invalid thread access errors in multithreaded GUI programs. 
Any call graph construction algorithm can be used (line 2). The algorithm
is parameterized by the three methods in lines 3--5 which are specific to each GUI framework
 as described in Section~\ref{sec:platforms}.
} \label{fig:detectalgorithm}
\end{figure}

Given a sound call graph, our algorithm is sound in that it does not
miss true positives. We note, however, that computing a sound
call graph in the presence of reflection is non-trivial. 
In particular, GUI applications built on some popular frameworks like Android
often use configuration files and reflection to specify GUI layout.
To alleviate this problem, we next proposed a reflection-aware call graph
construction algorithm in Section~\ref{sec:cg}.

@@

In an object-oriened language wth dynamic dispatch, the
crucial step in constructing a call graph is to compute a conservative
approximation of the set of methods that can be invoked by a given
virtual method call. Call graph construction algorithms have been
studied intensively in the 1990s. While their original formulations
use a variety of formalisms, most of them can be recast as set-based
analyses. Various algorithms differ primarily in the number of sets
that are used to approximate run-time values of expressions. 
In practice, algorithms such as RTA that use a single set for the whole
program scale well but achieves relatively lower precision.  The
k-CFA algorithms maintains one or several sets per expression achieves better
precision than RTA (\textit{k} is length of calling context).

%this is wrong for k-CFA, k-CFA maintains several sets per expression, which k > 0
%should cite Ben Livshit's paper on "Reflection analysis for Java"
%Donot overclaim "say propose a new technique", instead, say "refine the technique"
%also need to cite Yannis's paper on solving k-CFA paradox

%\textbf{need to describe why need to traverse from the UI entry, not just from the thread entry}

@@

Unfortunately, GUI applications often use reflection extensively and make
existing call graph construction algorithms such as RTA and k-CFA
fail to build a sufficiently complete call graph.
The example code in Figure~\ref{fig:sampleandroid} from an Android application
 illustrates the limitations.
In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the associated XML file. When this button
is clicked, its event handling code (lines 9--11) updates the text.
%d caches
%the current view to a list declared at line 2.

@@

To address this limitation, we present an algorithm to construct
a reflection-aware call graph based on simple program transformation.
The basic idea to replace reflection calls with explicit object
creation statements, pretending that the corresponding concrete object
has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
It consists of two steps. The first step is a simple program
transformation to replace reflection calls with object creation statements, and
the second step is to use a standard call graph construction algorithm
to construct the graph on the transformed program. The reflection call
represents a method invocation that relies Java reflection to create
objects, such as the \CodeIn{findViewById} method in Android applications.
In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
the first step of program transformation. The algorithm iterates through every statement
in an analyzed program. When it sees a reflection call, the algorithm analyzes the
program to determine a set of possible classes that might be created.
After that, the algorithm creates a new statement which non-deterministically
returns a new object from the object set. Line 8 is the second step
to build a call graph on the transformed program.  In this step,
any existing call graph construction algorithms can be used.

The algorithm in Figure~\ref{fig:cgalgorithm} is parameterized in three places:
line 2, line 3, and line 8. We instantiated it for Android applications as
follows. On line 2, the predicate $isReflectionCall$ returns true
if the $statement$ is a \CodeIn{findViewById(id)} method call. On line 3, method
\CodeIn{getAllObjectsThatMaybeCreated} parses the associated XML configuration
file in an Android application to extract the class declaration
 correspondinig to the \CodeIn{id} value. If the \CodeIn{id}
value is dynamically generated, the method will conservatively
return all subclasses of the declared type. On line 8, any existing
call graph construction algorithm can be used to build the call graph
on top of the transformed program.

For the example in Figure~\ref{fig:sampleandroid}, the algorithm
first parses the XML configuration file to determine that the \CodeIn{button\_id}
value is mapped to a \CodeIn{Button} instance declaration. Then it
replaces the reflection call: \CodeIn{findViewById(R.id.button\_id)} 
with an explicit object creation call: \CodeIn{new Button(null)}.
After that, the algorithm employs existing call graph construction
algorithms to analyze the transformed program, and permits them
to add the call edge \CodeIn{setText} to the resulting graph.

@@

%\item
\textbf{4. Filter Report With the Same $k$ Head Methods}. A method can call
multiple methods that access GUI objects, such as:
\begin{CodeOut}
\begin{alltt}
     public void m() \{
         accessUIObject1();
         accessUIObject2();
     \}
\end{alltt}
\end{CodeOut}
If method \CodeIn{m()} is invoked by a non-UI thread, method call chains
only different at the last few method nodes may be reported separately, such as:

@@

We instantiated our error detection techniques for four popular GUI frameworks,
namely SWT, Eclipse plugin environment, Swing, and Android.
The major framework-specific parts, corresponding to
lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
and \textbf{safe methods} for each framework.

%For each framework, we customize the \textit{call graph entry nodes},
%\textit{UI-accessing nodes}, and \textit{safe methods} on lines 3 -- 5 of the
%algorithm in

@@

%customizing for: entry points, starting points, error checking, thread
%safe methods, what is the event dispatching thread?

@@

\item \textbf{Safe methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
and \CodeIn{Display.syncExec}) to execute code (a)synchro-
nizedly on the UI thread.
 We treat these two methods as safe methods, since invoking
them from any thread 
%are generally considered to be safe and
will not cause an invalid thread access error.

@@

\item \textbf{UI-accessing nodes} and \textbf{Safe methods} are the same as SWT.

@@

\item \textbf{Safe methods: }  Swing's two helper methods
(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code in the UI thread.

@@

\item \textbf{Safe methods: } two helper methods (\CodeIn{View.post}
and \CodeIn{View.postDelay}) that execute code on the UI thread. 
Invoking them on any thread will not cause an invalid thread access error.
%Invoking these two methods are generally considered to be safe, and would not
%cause an invalid thread access error.

>>>>

This section formulates the problem. We first define the
notations of \textit{UI thread}, \textit{non-UI threads},
\textit{UI-accessing methods},
 \textit{safe UI methods}, and \textit{invalid thread access error}, and
state two assumptions we make with regard to error detection.

@@

\noindent {\textsc{\textbf{Assumption 1.}}} {We assume that each multithreaded
GUI application has a single global UI thread. This is true for applications
built on top of GUI frameworks adopting the single-GUI-thread rule. The
only exception is that 
 an application may fork a new process to launch another
application with its own UI thread. In that case, we require the
launched application to be analyzed separately.}\vspace{1mm}

@@

\noindent  {\textsc{\textbf{Definition 4 (Safe UI Methods).}}} {GUI frameworks that
adopt the single-GUI-thread rule must provide methods to permit non-UI threads
to run code in the UI thread. We call such methods \textit{safe UI methods}, since
they can be invoked safely by any thread.}\vspace{1mm}

\noindent  {\textsc{\textbf{Definition 5 (Invalid Thread Access).}}} {An invalid
thread access error occurs when the UI thread may spawn a non-UI thread, and there
exists a path from the non-UI thread's \CodeIn{start} method to any UI-accessing method
without going through any safe UI method. }\vspace{2mm}

@@

Our algorithm in Figure~\ref{fig:detectalgorithm} %works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes, UI-accessing nodes, and safe nodes
for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
As an example, for a SWT desktop application, the entry nodes include
the single main method, UI-accessing nodes include all methods that
call method \CodeIn{Display.checkWidget} or \CodeIn{Display.checkDevice},
and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
\CodeIn{Display.syncExec} for message passing. The detailed instantiation
for each supported framework is explained in Section~\ref{sec:platforms}.

For each entry node, the algorithm uses standard Breadth First Search (BFS)
to find all reachable \CodeIn{Thread.start()} nodes (line 7).
Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
non-UI thread is spawned.  After that, from each \CodeIn{Thread.start()}
node, the algorithm uses BFS again to find reachable UI-accessing methods (lines 9 -- 28).
Specifically, it uses a queue to keep track of nodes to be visited (line 9),
and stores all visited nodes to avoid infinite loop (line 10).
The algorithm checks every successive node to be visited (line 18);
it reports an error if that node is a UI-accessing method (lines 20, 21), or skips
it if it is a safe UI method (lines 22, 23), or simply keeps traversing otherwise (line 25).

Note that when the algorithm determines that a UI-accessing method may be invoked
by a non-UI thread, it computes a method call chain from the entry node to
the UI-accessing node as the error report.
The method \CodeIn{createErrorReport} on line 20 does that. 
Figure~\ref{fig:androiderror} shows a method call chain from the entry
node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{recomputeViewAttributes}
(for the sake of clarification, we also show the checking method \CodeIn{checkThread} in the reported warning).

\begin{figure}[t]
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a set of potential invalid thread access $\mathit{errors}$\\
%\textbf{Auxiliary Methods:}\\
%getSuccNodes($\mathit{g}$, $\mathit{n}$): return node $\mathit{n}$'s successive
%nodes in the graph $\mathit{g}$\\
\vspace{-4mm}
\begin{algorithmic}[1]
\STATE $\mathit{errors}$ $\leftarrow$ $\emptyset$
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
\STATE $\mathit{uiAccessNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
\STATE $\mathit{safeNodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)
\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
\STATE $\mathit{threadStartNodes}$ $\leftarrow$ getReachableStartsByBFS($\mathit{cg}$)
\FOR{each $\mathit{threadStart}$ in $\mathit{threadStartNodes}$}
\STATE $\mathit{fringe}$ $\leftarrow$ an empty queue\\
\COMMENT{keep all visited nodes to avoid infinite loop}
\STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
\STATE $\mathit{fringe}$.enqueue(getSuccNodes($\mathit{cg}$, $\mathit{threadStart}$))
\WHILE{$\mathit{fringe}$.isNotEmpty()}
\STATE $\mathit{node}$ $\leftarrow$ $\mathit{fringe}$.dequeue()
\IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
\STATE continue
\ENDIF
\STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
\FOR{each $\mathit{succNode}$ in getSuccNodes($\mathit{cg}$, $\mathit{node}$)}
\IF{$\mathit{succNode}$ $\in$ $\mathit{uiAccessNodes}$}
\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{entryNode, succNode}$)
\STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
\ELSIF{$\mathit{succNode}$ $\in$ $\mathit{safeNodes}$}
\STATE continue
\ELSE
\STATE $\mathit{fringe}$.enqueue($\mathit{succNode}$)
\ENDIF 
\ENDFOR
\ENDWHILE
\ENDFOR
\ENDFOR
\RETURN $errors$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\caption{Algorithm for detecting invalid thread access errors in multithreaded GUI programs. 
Any call graph construction algorithm can be used (line 2). The algorithm
is parameterized by the three methods in lines 3--5 which are specific to each GUI framework
 as described in Section~\ref{sec:platforms}.
} \label{fig:detectalgorithm}
\end{figure}

The algorithm in Figure~\ref{fig:detectalgorithm} uses BFS to search
for potential error-revealing paths, since BFS always returns the
shortest path from the entry node to the UI-accessing node, and thus
permits to produce small error reports. However,
other graph search strategies such as Depath-First Search (DFS) or
exhaustive path search can also be employed. In our evaluation (Section~\ref{sec:search}),
we empirically compared three different graph search strategies, and demonstrate that
using BFS allows the algorithm to find more errors than DFS and
exhaustive path search.
Given a sound call graph, our algorithm is sound in that it does not
miss true positives. We note, however, that computing a sound
call graph in the presence of reflection is non-trivial. 
To alleviate this problem, we next proposed a reflection-aware call graph
construction algorithm in Section~\ref{sec:cg}.

@@

@@

GUI applications tend to use reflection intensively. In particular, GUI applications built on 
top of the Android framework often use configuration files and reflection to specify GUI layout.
The heavy use of reflection makes many existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
The example code in Figure~\ref{fig:sampleandroid} from an Android application
 illustrates the limitations.
In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the associated XML file. When this button
is clicked, its event handling code (lines 9--11) updates the text.
%d caches
%the current view to a list declared at line 2.

@@

To address this limitation, we present an algorithm to construct
a reflection-aware call graph based on simple program transformation.
The basic idea to replace reflection calls with explicit object
creation statements, pretending that the corresponding concrete object
has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
It consists of two steps. The first step is a simple program
transformation to replace reflection calls with object creation statements, and
the second step is to use an existing call graph construction algorithm
to build the graph on the transformed program. In our context,
a reflection call represents a framework-specific helper method invocation
that uses Java reflection to create desirable objects, such as
the \CodeIn{findViewById} method in Android applications, instead
of the methods in the \CodeIn{java.lang.reflection} package.
In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
the first step of program transformation. The algorithm iterates through every statement
in an analyzed program. When it sees a reflection call, the algorithm
determines a set of possible objects that might be created.
After that, the algorithm creates a statement which non-deterministically
returns a new object from the object set. Line 8 is the second step
to build a call graph on the transformed program.

This algorithm is parameterized in three places:
line 2, line 3, and line 8. Currently, we instantiated it
for Android applications as follows. On line 2,
the predicate isReflectionCall returns true
if the $statement$ is a \CodeIn{findViewById(id)} method call. On line 3, method
\CodeIn{getAllObjectsThatMaybeCreated} parses the associated XML configuration
file in an Android application to extract the class declaration
 correspondinig to the given \CodeIn{id} value. If the \CodeIn{id}
value is dynamically generated, the method will conservatively
return instances of all subclasses of the declared type.
On line 8, any existing call graph construction algorithm can be directly
used.

Take the code in Figure~\ref{fig:sampleandroid} as an example.
When the algorithm sees the reflection call
\CodeIn{findViewById(R.id.button\_id)}, it
parses the XML configuration file to determine that the \CodeIn{button\_id}
value is mapped to a \CodeIn{Button} instance. Then, it
replaces the reflection call
with an explicit object creation statement: \CodeIn{new Button(null)}.
After that, the algorithm employs existing call graph construction
algorithms to analyze the transformed program, and permits them
to add the call edge \CodeIn{setText} to the resulting graph.

@@

%\item
\textbf{4. Filter Report With the Same $k$ Head Methods}. A method can call
multiple methods that access GUI objects, such as:

\begin{CodeOut}
\begin{alltt}
     public void m() \{
         accessUIObject1();
         accessUIObject2();
     \}
\end{alltt}
\end{CodeOut}
If method \CodeIn{m()} is invoked by a non-UI thread, method call chains
only different at the last few method nodes may be reported separately, such as:

@@

We instantiated our error detection techniques for four popular GUI frameworks,
namely SWT, Eclipse plugin environment, Swing, and Android.
The major framework-specific parts, corresponding to
lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
and \textbf{safe UI methods} for each framework.

%For each framework, we customize the \textit{call graph entry nodes},
%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
%algorithm in

@@

%customizing for: entry points, starting points, error checking, thread
%safe UI methods, what is the event dispatching thread?

@@

\item \textbf{Safe UI methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
and \CodeIn{Display.syncExec}) to execute code (a)synchro-
nizedly on the UI thread.
 We treat these two methods as safe UI methods, since invoking
them from any thread 
%are generally considered to be safe and
will not cause an invalid thread access error.

@@

\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.

@@

\item \textbf{Safe UI methods: }  Swing's two helper methods
(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code in the UI thread.

@@

\item \textbf{Safe UI methods: } two helper methods (\CodeIn{View.post}
and \CodeIn{View.postDelay}) that execute code on the UI thread. 
Invoking them on any thread will not cause an invalid thread access error.
%Invoking these two methods are generally considered to be safe, and would not
%cause an invalid thread access error.
